The Impact of Educational Expenses of New Coders

### 2021-04-17 outputs/paper/paper.Rmd
Edit regression analysis

```{r, results='asis'}
#### Multiple regression analysis ####
fit.lm <- lm(formula = 
               MoneyForLearning ~ 
               Gender +
               CityPopulation +
               CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

# summary(fit.lm)
stargazer::stargazer(fit.lm, 
          title = "Result of regression model", 
          header = FALSE,
          type = "latex")
```

```{r}
#### Beta ####
QuantPsyc::lm.beta(fit.lm)
```

@@

### VIF
car::vif(fit.lm)
### Tolerance
1/car::vif(fit.lm)
```

>>>>

```{r, results='asis'}
#### Multiple regression analysis ####
multiReg1 <- lm(formula = 
               MoneyForLearning ~ 
               CityPopulation +
               CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

multiReg2 <- lm(formula = 
               MoneyForLearning ~ 
               Age +
               CityPopulation +
               CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

multiReg3 <- lm(formula = 
               MoneyForLearning ~ 
               Gender +
               Age +
               CityPopulation +
               CommuteTime +
               Income +
               MonthsProgramming +
               SchoolDegree, 
               data = dfNewCoders)

# summary(multiReg3)
stargazer::stargazer(multiReg1, multiReg2, multiReg3, 
          title = "Result of regression model", 
          header = FALSE,
          type = "latex")
```

```{r}
#### Beta ####
QuantPsyc::lm.beta(multiReg3)
```

@@

### VIF
car::vif(multiReg3)
### Tolerance
1/car::vif(multiReg3)
```
